---
title: "BSA Research"
author: "Sean Lashkari, Arjun Parikh"
date: "2/20/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include = FALSE}
library(tidyverse)
```

Make sure `rates.csv`, `run_pct.csv`, and `hr_pct.csv` are in your working directory.
```{r, include = FALSE}
rates_df <- read_csv("rates.csv")
run_pct <- read_csv("run_pct.csv")
hr_pct <- read_csv("hr_pct.csv")
```



Here are two t-tests. The first is testing for a difference between the proportion of runs scored at home before and after a fence change for all teams. The second is testing for a difference between the proportion of home runs scored at home before and after a fence change for all teams.
```{r}
x <- filter(run_pct, flag == "before", location == "home") %>% select(run_percent)
y <- filter(run_pct, flag == "after", location == "home") %>% select(run_percent)
t.test(x$run_percent, y$run_percent)

x <- filter(hr_pct, flag == "before", location == "home") %>% select(hr_percent)
y <- filter(hr_pct, flag == "after", location == "home") %>% select(hr_percent)
t.test(x$hr_percent, y$hr_percent)
```

We obtain two very large p-values. According to the tests, we have no evidence that there is a difference between the proportion of runs and home runs scored at home before and after a dimension change. We will now graphically explore run proportions scored at home for each team.



# Houston Astros
```{r, echo = FALSE}
par(mfrow = c(1, 2))

# run pct boxplot
box_df <- run_pct %>% filter(location == "home", team == "HOU") # make df suitable for boxplots
box_df$flag <- factor(box_df$flag, levels = c("before", "after")) # intuitively order the plots
boxplot(run_percent ~ flag, col = "orange", data = box_df, 
        xlab = "Time Relative to Fence Change", ylab = "Proportion of Runs Scored at Home",
        main = "Houston Astros")

# home run pct boxplot
box_df <- hr_pct %>% filter(location == "home", team == "HOU") # make df suitable for boxplots
box_df$flag <- factor(box_df$flag, levels = c("before", "after")) # intuitively order the plots
boxplot(hr_percent ~ flag, col = "orange", data = box_df, 
        xlab = "Time Relative to Fence Change", ylab = "Proportion of Home Runs at Home",
        main = "Houston Astros")
```

# Miami Marlins
```{r, echo = FALSE}
par(mfrow = c(1, 2))

# run pct boxplot
box_df <- run_pct %>% filter(location == "home", team %in% c("FLA", "MIA"))
box_df$flag <- factor(box_df$flag, levels = c("before", "after")) # intuitively order the plots
boxplot(run_percent ~ flag, col = "cyan", data = box_df, 
        xlab = "Time Relative to Fence Change", ylab = "Proportion of Runs Scored at Home",
        main = "Miami Marlins")

# home run pct boxplot
box_df <- hr_pct %>% filter(location == "home", team %in% c("MIA", "FLA")) # make df suitable for boxplots
box_df$flag <- factor(box_df$flag, levels = c("before", "after")) # intuitively order the plots
boxplot(hr_percent ~ flag, col = "cyan", data = box_df, 
        xlab = "Time Relative to Fence Change", ylab = "Proportion of Home Runs at Home",
        main = "Miami Marlins")
```

# San Diego Padres
```{r, echo = FALSE}
par(mfrow = c(1, 2))

# run pct boxplot
box_df <- run_pct %>% filter(location == "home", team == "SDP")
box_df$flag <- factor(box_df$flag, levels = c("before", "after")) # intuitively order the plots
boxplot(run_percent ~ flag, col = "darkgoldenrod", data = box_df, 
        xlab = "Time Relative to Fence Change", ylab = "Proportion of Runs Scored at Home",
        main = "San Diego Padres")

# home run pct boxplot
box_df <- hr_pct %>% filter(location == "home", team == "SDP") # make df suitable for boxplots
box_df$flag <- factor(box_df$flag, levels = c("before", "after")) # intuitively order the plots
boxplot(hr_percent ~ flag, col = "darkgoldenrod", data = box_df, 
        xlab = "Time Relative to Fence Change", ylab = "Proportion of Home Runs at Home",
        main = "San Diego Padres")
```

# Seattle Mariners
```{r, echo = FALSE}
par(mfrow = c(1, 2))

# run pct boxplot
box_df <- run_pct %>% filter(location == "home", team == "SEA")
box_df$flag <- factor(box_df$flag, levels = c("before", "after")) # intuitively order the plots
boxplot(run_percent ~ flag, col = "darkslategray", data = box_df, 
        xlab = "Time Relative to Fence Change", ylab = "Proportion of Runs Scored at Home",
        main = "Seattle Mariners")

box_df <- hr_pct %>% filter(location == "home", team == "SEA") # make df suitable for boxplots
box_df$flag <- factor(box_df$flag, levels = c("before", "after")) # intuitively order the plots
boxplot(hr_percent ~ flag, col = "darkslategray", data = box_df, 
        xlab = "Time Relative to Fence Change", ylab = "Proportion of Home Runs at Home",
        main = "Seattle Mariners")
```

# Atlanta Braves
```{r, echo = FALSE}
par(mfrow = c(1, 2))

# run pct boxplot
box_df <- run_pct %>% filter(location == "home", team == "ATL")
box_df$flag <- factor(box_df$flag, levels = c("before", "after")) # intuitively order the plots
boxplot(run_percent ~ flag, col = "darkred", data = box_df, 
        xlab = "Time Relative to Fence Change", ylab = "Proportion of Runs Scored at Home",
        main = "Atlanta Braves")

# home run pct boxplot
box_df <- hr_pct %>% filter(location == "home", team == "ATL") # make df suitable for boxplots
box_df$flag <- factor(box_df$flag, levels = c("before", "after")) # intuitively order the plots
boxplot(hr_percent ~ flag, col = "darkred", data = box_df, 
        xlab = "Time Relative to Fence Change", ylab = "Proportion of Home Runs at Home",
        main = "Atlanta Braves")
```

# Minnesota Twins
```{r, echo = FALSE}
par(mfrow = c(1, 2))

# run pct boxplot
box_df <- run_pct %>% filter(location == "home", team == "MIN")
box_df$flag <- factor(box_df$flag, levels = c("before", "after")) # intuitively order the plots
boxplot(run_percent ~ flag, col = "steelblue4", data = box_df, 
        xlab = "Time Relative to Fence Change", ylab = "Proportion of Runs Scored at Home",
        main = "Minnesota Twins")

# home run pct boxplot
box_df <- hr_pct %>% filter(location == "home", team == "MIN") # make df suitable for boxplots
box_df$flag <- factor(box_df$flag, levels = c("before", "after")) # intuitively order the plots
boxplot(hr_percent ~ flag, col = "steelblue4", data = box_df, 
        xlab = "Time Relative to Fence Change", ylab = "Proportion of Home Runs at Home",
        main = "Minnesota Twins")
```

